Beyond conceptual eco-physiological hypotheses: insights from a general size and trait-based model of ectotherm thermal performance

### 2018-03-20 draft_model_only.Rnw
Feb 5th draft

ggsc <- ggplot(sc_act) + 
  geom_line(aes(x=Temperature, y=value, linetype=Activity,col=Activity)) +
  theme_cowplot()+
  scale_color_manual(values = cols, guide='none')+
  scale_linetype(guide='none')+
  facet_wrap(~Dispatch,ncol = 1,labeller = lab1)+
  theme(strip.text = element_text(hjust = 0),
        strip.background = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank()) + 
  labs(x = expression("Mean temperature " ( degree*C)),
       y=expression('Activity ' (tau)))

@@

ggso <- sco %>%
  ggplot() + 
   geom_line(aes(x=Temperature, y=value, linetype=Metabolism,col=Metabolism)) +
  theme_cowplot()+
  scale_color_manual(values = cols, guide='none')+
  scale_linetype(guide='none')+
  facet_wrap(~Dispatch,ncol = 1,labeller = lab2)+
  theme(strip.text = element_text(hjust = 0),
        strip.background = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank()) + 
  labs(x = expression("Mean temperature " ( degree*C)),
       y=expression(Oxygen~(mg.yr^-1)))

@@

ggplot(sc_acts) + 
  geom_line(aes(x=Temperature, y=value, linetype=Activity,col=Activity)) +
  theme_cowplot()+
  scale_color_manual(values = cols, guide='none')+
  scale_linetype(guide='none')+
  facet_wrap(~Dispatch,ncol = 2,labeller = laba)+
  theme(strip.text = element_text(hjust = 0),
        strip.background = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank()) + 
  labs(x = expression("Mean temperature " ( degree*C)),
       y=expression('Activity ' (tau)))

@@

ggplot(sc_feed) + 
  geom_line(aes(x=Temperature, y=value, linetype=Rate,col=Rate,group=Rate)) +
  theme_cowplot()+
  facet_wrap(~Dispatch,labeller = lab,ncol=2)+
  theme(strip.text = element_text(hjust = 0),
        strip.background = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank())+
  scale_linetype_manual(values=c(1:4,1),guide='none')+
  scale_color_manual(values = cols,guide='none')+
  labs(x = expression("Mean temperature " ( degree*C)),
       y='Relative rate')

@@

gouts <- parallel::mclapply(scs,plot_data_growth_tO2,mc.cores = 2)

@@

ggplot() +
  geom_line(aes(x=t, y=t_length,col=Temperature,group=as.factor(Temperature)),data=t_growth) +
  geom_point(aes(x=ts, y=m),data=norm) +
  # geom_point(aes(x=tsq1, y=mq1),data=norm,col=cols[3]) +
  # geom_point(aes(x=tsq3, y=mq3),data=norm,col=cols[3]) +
  #geom_point(data=growth_scenarios[seq.int(1,nrow(growth_scenarios),by = 5),],aes(x=Temperature, y=Temp, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
  theme_cowplot()+
  facet_wrap(~Dispatch,scales='free',ncol=2,labeller = lab)+
  viridis::scale_colour_viridis(expression(Temp~(degree*C)))+
  theme(legend.text = element_text(size=8),
        legend.title = element_text(size=9),
        strip.text = element_text(hjust = 0),
        strip.background = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank())+
  coord_cartesian()+
  labs(y = 'Length (cm)',
       x='Age  (years)')

@@

f1 <- ggplot(R0s) + 
  geom_line(aes(x=Temperature, y=R0, linetype=Scenario,col=O2lim,group=Dispatch)) +
  theme_cowplot()+
  theme(
        panel.background = element_blank(),
        plot.background = element_blank())+
  scale_linetype_manual(values=c(1:4),guide='none')+
  scale_color_manual(values = cols,guide='none')+
  labs(x = '',
       y=expression('R0/R0'[max])) +
    theme(axis.title.x=element_blank(),
          axis.text.x = element_text(colour = NA))

>>>>

ggsc <- ggplot(sc_act %>% filter(Dispatch=='M strategy Domed')) + 
  geom_line(aes(x=Temperature, y=value, linetype=Activity,col=Activity)) +
  theme_cowplot()+
  scale_color_manual(values = cols)+
  scale_linetype()+
  #facet_wrap(~Dispatch,ncol = 1,labeller = lab1)+
  theme(strip.text = element_text(hjust = 0),
        strip.background = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank()) + 
  labs(x = expression("Mean temperature " ( degree*C)),
       y=expression('Activity ' (tau)))

@@

ggso <- sco  %>% filter(Dispatch=='M strategy Domed') %>%
  ggplot() + 
   geom_line(aes(x=Temperature, y=value, linetype=Metabolism,col=Metabolism)) +
  theme_cowplot()+
  scale_color_manual(values = cols)+
  scale_linetype()+
  #facet_wrap(~Dispatch,ncol = 1,labeller = lab2)+
  theme(strip.text = element_text(hjust = 0),
        strip.background = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank()) + 
  labs(x = expression("Mean temperature " ( degree*C)),
       y=expression(Oxygen~(mg.yr^-1)))

@@

ggplot(sc_acts %>% filter(Dispatch=='P strategy Large')) + 
  geom_line(aes(x=Temperature, y=value, linetype=Activity,col=Activity)) +
  theme_cowplot()+
  scale_color_manual(values = cols)+
  scale_linetype()+
  #facet_wrap(~Dispatch,ncol = 2,labeller = laba)+
  theme(strip.text = element_text(hjust = 0),
        strip.background = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank()) + 
  labs(x = expression("Mean temperature " ( degree*C)),
       y=expression('Activity ' (tau)))

@@

ggplot(sc_feed%>% filter(Dispatch=='M strategy Domed')) + 
  geom_line(aes(x=Temperature, y=value, linetype=Rate,col=Rate,group=Rate)) +
  theme_cowplot()+
  #facet_wrap(~Dispatch,labeller = lab,ncol=2)+
  theme(strip.text = element_text(hjust = 0),
        strip.background = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank())+
  scale_linetype_manual(values=c(1:4,1))+
  scale_color_manual(values = cols)+
  labs(x = expression("Mean temperature " ( degree*C)),
       y='Relative rate')

@@

gouts <- parallel::mclapply(scs[2],plot_data_growth_tO2,mc.cores = 2)

@@

ggplot() +
  geom_line(aes(x=t, y=t_length,col=Temperature,group=as.factor(Temperature)),data=t_growth) +
  #geom_point(aes(x=ts, y=m),data=norm) +
  # geom_point(aes(x=tsq1, y=mq1),data=norm,col=cols[3]) +
  # geom_point(aes(x=tsq3, y=mq3),data=norm,col=cols[3]) +
  #geom_point(data=growth_scenarios[seq.int(1,nrow(growth_scenarios),by = 5),],aes(x=Temperature, y=Temp, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
  theme_cowplot()+
  #facet_wrap(~Dispatch,scales='free',ncol=2,labeller = lab)+
  viridis::scale_colour_viridis(expression(Temp~(degree*C)))+
  theme(legend.text = element_text(size=8),
        legend.title = element_text(size=9),
        strip.text = element_text(hjust = 0),
        strip.background = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank())+
  coord_cartesian()+
  labs(y = 'Length (cm)',
       x='Age  (years)')

@@

f1 <- ggplot(R0s) + 
  geom_line(aes(x=Temperature, y=R0, linetype=Scenario,col=O2lim,group=Dispatch)) +
  theme_cowplot()+
  theme(
        panel.background = element_blank(),
        plot.background = element_blank())+
  scale_linetype_manual(values=c(1:4),guide='none')+
  scale_color_manual(values = cols,guide='none')+
  labs(x = expression("Mean temperature " ( degree*C)),
       y=expression('R0/R0'[max]))
